### 2023-04-17 README.Rmd
add info that Apptainer/Singularity containers with RStudio IDE cannot be started using `root` user
update README: (1) compatibility with old RStudio IDE (<4.0) that requires binding .rstudio to the container (2) add default port parameter so that it is obvious how to change it

```bash
mkdir -p run var-lib-rstudio-server
printf 'provider=sqlite\ndirectory=/var/lib/rstudio-server\n' > database.conf
```

After that, you can run the container:

```bash
apptainer exec \
    --env PASSWORD='set_your_password' \
    --bind run:/run,var-lib-rstudio-server:/var/lib/rstudio-server,database.conf:/etc/rstudio/database.conf \
    container.sif \
    /usr/lib/rstudio-server/bin/rserver \
    --auth-none=0 --auth-pam-helper-path=pam-helper \
    --server-user=$(whoami)
```

@@

```bash
singularity exec \
    --env PASSWORD='set_your_password' \
    --bind run:/run,var-lib-rstudio-server:/var/lib/rstudio-server,database.conf:/etc/rstudio/database.conf \
    container.sif \
    /usr/lib/rstudio-server/bin/rserver \
    --auth-none=0 --auth-pam-helper-path=pam-helper \
    --server-user=$(whoami)
```

The default port is 8787, you can also change the port by adding `--www-port=` in the end of the line above (e.g. `--www-port=8080`).

>>>>

```bash
mkdir -p run var-lib-rstudio-server .rstudio
printf 'provider=sqlite\ndirectory=/var/lib/rstudio-server\n' > database.conf
```

After that, you can run the container (do not run as `root` user, otherwise you will not be able to login to RStudio IDE):

```bash
apptainer exec \
    --env PASSWORD='set_your_password' \
    --bind run:/run,var-lib-rstudio-server:/var/lib/rstudio-server,database.conf:/etc/rstudio/database.conf,.rstudio:/home/rstudio/.rstudio/ \
    container.sif \
    /usr/lib/rstudio-server/bin/rserver \
    --auth-none=0 --auth-pam-helper-path=pam-helper \
    --server-user=$(whoami) --www-port=8787
```

@@

```bash
singularity exec \
    --env PASSWORD='set_your_password' \
    --bind run:/run,var-lib-rstudio-server:/var/lib/rstudio-server,database.conf:/etc/rstudio/database.conf,.rstudio:/home/rstudio/.rstudio/ \
    container.sif \
    /usr/lib/rstudio-server/bin/rserver \
    --auth-none=0 --auth-pam-helper-path=pam-helper \
    --server-user=$(whoami) --www-port=8787
```
